TEMPERATURES AND METALLICITIES OF M DWARFS IN THE \apogee\ SURVEY

### 2019-08-01 paper/draft.tex
add ruwe ref

\item \textbf{Astrometric cut:} Using the \gaia\ re-normalised unit weight error (RUWE), a metric of evaluating the fit of the astrometric solution described in the additional release notes, we apply a cut of ${\rm RUWE}<1.2$ to remove sources with high astrometric error or noise, such as binaries (see Figure \ref{fig:ruwe_cut}).

>>>>

\item \textbf{Astrometric cut:} Using the \gaia\ re-normalised unit weight error (RUWE), a metric of evaluating the fit of the astrometric solution described in the additional release notes \citep{Lindgren:2018}, we apply a cut of ${\rm RUWE}<1.2$ to remove sources with high astrometric error or noise, such as binaries (see Figure \ref{fig:ruwe_cut}).
